---
title: "Assignment_07_26_2017"
author: "Ruijuan Li"
date: "7/21/2017"
output: 
  html_document: 
    keep_md: yes
---

# 15.3.1 Exercise

1. Explore the distribution of rincome (reported income). What makes the default bar chart hard to understand? How could you improve the plot?
```{r}
library(tidyverse)

ggplot(gss_cat, aes(x=rincome)) +
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, size = 8))  
```

2. What is the most common relig in this survey? What’s the most common partyid?
```{r}
gss_cat %>% 
  group_by(relig) %>%
  count() %>%
  arrange(desc(n)) %>%
  head(1)

gss_cat %>% 
  group_by(partyid) %>%
  count() %>%
  arrange(desc(n)) %>%
  head(1) 
```

3. Which relig does denom (denomination) apply to? How can you find out with a table? How can you find out with a visualisation?
```{r}
colnames(gss_cat)
gss_cat %>%
  select(relig, denom) %>%
  unique()  
```

# 15.4.1 Exercises

There are some suspiciously high numbers in tvhours. Is the mean a good summary? 

For each factor in gss_cat identify whether the order of the levels is arbitrary or principled.

Why did moving “Not applicable” to the front of the levels move it to the bottom of the plot?


