---
title: "Assignment_05_31_2017"
author: "Ruijuan Li"
date: "5/28/2017"
output: 
  html_document: 
    keep_md: yes
---

10.5 Exercises

1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).
```{r}
library(ggplot2)
library(tidyverse)
class(mtcars)
```

2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

      df <- data.frame(abc = 1, xyz = "a")
      df$x
      df[, "xyz"] 
      df[, c("abc", "xyz")] 

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x # I even don't know this before! 
class(df[, "xyz"]) 
df[, c("abc", "xyz")] 

test <- tibble(abc = 1, xyz = "a")
test[["xyz"]] 

# compared to data.frame, tibble, cannot do subsetting using [], it returns another tibble, and tibble doens't do partial matching.  
```

3. If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?
```{r}
# tibble[["mpg"]]
```

4. Practice referring to non-syntactic names in the following data frame by:

      1. Extracting the variable called 1.

      2. Plotting a scatterplot of 1 vs 2.

      3. Creating a new column called 3 which is 2 divided by 1.

      4. Renaming the columns to one, two and three.

```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```

```{r}
# 1) 
annoying[["2"]]
# 2) 
ggplot(annoying) + geom_point(aes(annoying$`1`, annoying$`2`))
# 3) 
annoying2 <- mutate(annoying, `3` = `2`/`1`)
# 4) 
colnames(annoying2) <- c("one", "two", "three")
View(annoying2)
```

5. What does tibble::enframe() do? When might you use it?
```{r}
?enframe # enframe() converts named atomic vectors or lists to two-column data frames. For unnamed vectors, the natural sequence is used as name column. 
enframe(1:3)
enframe(c(a = 5, b = 7))
```

6. What option controls how many additional column names are printed at the footer of a tibble?
```{r}
nycflights13::flights %>% 
  print(n = 3, width = Inf) # n for rows, width = Inf print all columns  

nycflights13::flights %>% 
  print(n = 3, width = NULL, n_extra = 2)  
nycflights13::flights %>% 
  print(n = 3, width = NULL, n_extra = 7)  
# n_extra 
```



