---
title: "Assignment_06_07_2017"
author: "Ruijuan Li"
date: "6/3/2017"
output: 
  html_document: 
    keep_md: yes
---

# 11.2.2 Exercises

```{r, results='hide', warning=FALSE}
library(tidyverse)
```

1. What function would you use to read a file where fields were separated with
“|”?

      read_delim(file, delim = "|")


2. Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

      read_csv(file, col_names = TRUE, col_types = NULL,
  locale = default_locale(), na = c("", "NA"), quoted_na = TRUE,
  quote = "\"", comment = "", trim_ws = TRUE, skip = 0, n_max = Inf,
  guess_max = min(1000, n_max), progress = show_progress())

      read_tsv(file, col_names = TRUE, col_types = NULL,
  locale = default_locale(), na = c("", "NA"), quoted_na = TRUE,
  quote = "\"", comment = "", trim_ws = TRUE, skip = 0, n_max = Inf,
  guess_max = min(1000, n_max), progress = show_progress())
  
      delim; col_names; na; trim_ws, etc. 

3. What are the most important arguments to read_fwf()?

      read_fwf(file, col_positions, col_types = NULL, locale = default_locale(),
  na = c("", "NA"), comment = "", skip = 0, n_max = Inf,
  guess_max = min(n_max, 1000), progress = show_progress())

      col_positions; widths; start, end...
      
```{r}
fwf_sample <- readr_example("fwf-sample.txt")
cat(read_lines(fwf_sample))

# You can specify column positions in several ways:
# 1. Guess based on position of empty columns
read_fwf(fwf_sample, fwf_empty(fwf_sample, col_names = c("first", "last", "state", "ssn")))
# 2. A vector of field widths
read_fwf(fwf_sample, fwf_widths(c(20, 10, 12), c("name", "state", "ssn")))
# 3. Paired vectors of start and end positions
read_fwf(fwf_sample, fwf_positions(c(1, 30), c(10, 42), c("name", "ssn")))
# 4. Named arguments with start and end positions
read_fwf(fwf_sample, fwf_cols(name = c(1, 10), ssn = c(30, 42)))
# 5. Named arguments with column widths
read_fwf(fwf_sample, fwf_cols(name = 20, state = 10, ssn = 12))
# don't know how this can be useful for my analysis for this moment 
```

4. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?

```{r, results='hide'}
"x,y\n1,'a,b'"

x <- "x,y\n1,'a,b'"
read_delim(x, ",", quote = "'")
```

5. Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

```{r, results='hide', warning=FALSE}
read_csv("a,b\n1,2,3\n4,5,6")
read_csv("a,b,c\n1,2\n1,2,3,4")
read_csv("a,b\n\"1")
read_csv("a,b\n1,2\na,b")
read_csv("a;b\n1;3")
```