---
title: "Assignment_05_10_2017"
author: "Ruijuan Li"
date: "5/9/2017"
output: 
  html_document: 
    keep_md: yes
---

# import libs 
```{r}
library(nycflights13)
library(tidyverse)
colnames(flights)
```

# 5.2.4 Exercises
1) Find all flights that 
```{r}
# Had an arrival delay of two or more hours
arr_delay_over_2 <- filter(flights, arr_delay >= 120)
# Flew to Houston (IAH or HOU)
dest_houston <- filter(flights, dest == "IAH" | dest == "HOU")
# Were operated by United, American, or Delta
carrier_UA_AA_DL <- filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DL")
# Departed in summer (July, August, and September)
month_789 <- filter(flights, month == 7 | month == 8 | month == 9)
filter(flights, month %in% 7:9) 
# Arrived more than two hours late, but didn’t leave late
arr_delay_120_dep_delay_0 <- filter(flights, arr_delay > 120 & dep_delay <= 0)
# Were delayed by at least an hour, but made up over 30 minutes in flight
test <- filter(flights, dep_delay >= 60 & dep_delay-arr_delay > 30) 
# Departed between midnight and 6am (inclusive)
dep_time_midnight_6am <- filter(flights, dep_time >= 0 & dep_time <= 600)
```

2) Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?
```{r}
?between
dep_time_midnight_6am_2 <- filter(flights, between(dep_time, 0, 600)) 
identical(dep_time_midnight_6am, dep_time_midnight_6am_2)
```

3) How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
sum(is.na(flights$dep_time))
dep_time_missing <- flights[is.na(flights$dep_time),]
View(dep_time_missing) # dep_delay, arr_time, arr_delay, and air_time are all missing  
```

4) Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!) 
```{r}
NA ^ 0 # square 0 of any number is equal to 1 
NA | TRUE # | stands for OR, at least one TRUE leads to TRUE
FALSE & NA # & stands for AND, at least one FALSE leads to FALSE 
# the result of | and & must be "TRUE" or "FALSE"  
TRUE ^ 0
class(NA)
class(TRUE) 
```

# 5.3.1 Exercises
1) How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).
```{r}
arrange(flights, desc(is.na(dep_time)), dep_time) # don't understand...
arrange(flights, desc(is.na(dep_time))) 
```

2) Sort flights to find the most delayed flights. Find the flights that left earliest.
```{r}
head(arrange(flights, desc(dep_delay)), 1) 
head(arrange(flights, dep_time), 1)
```

3) Sort flights to find the fastest flights.
```{r}
head(arrange(flights, air_time), 1)
```

4) Which flights travelled the longest? Which travelled the shortest?
```{r}
head(arrange(flights, distance), 1)
tail(arrange(flights, distance), 1)
```

# 5.4.1 Exercises
1) Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
colnames(flights)
tmp <- select(flights, dep_time, dep_delay, arr_time, arr_delay)
```

2) What happens if you include the name of a variable multiple times in a select() call?
```{r}
dim(select(flights, dep_time, dep_time)) # only take once 
```

3) What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
?one_of # variables in charactor vector 
tmp2 <- select(flights, one_of(vars)) # this way we take 
colnames(tmp2) # we can predefine the specific column that we want to select 
```

4) Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
tmp3 <- select(flights, contains("TIME")) 
colnames(tmp3) 
tmp4 <- select(flights, contains("time"))
identical(tmp3, tmp4) # case insensitive 
# make it case sensitive 
select(flights, contains("TIME", ignore.case = F)) 
```

#5.5.2 Exercises

1) Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
colnames(flights)
head(flights$dep_time)
tmp5 <- mutate(flights, 
dep_time_2 = (dep_time %/% 100 * 60) +  (dep_time %% 100),
sched_dep_time_2 = (sched_dep_time %/% 100 * 60) +  (sched_dep_time %% 100)
)

head(tmp5[,c("dep_time", "dep_time_2", "sched_dep_time", "sched_dep_time_2")]) 
```

2) Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?
```{r}
tmp6<- mutate(flights,
          new = arr_time - dep_time)
tmp6[,c("arr_time", "new")] # not the same, they should be the same 

max(flights$arr_time, na.rm = T) 

?flights 
colnames(flights) 
summary(flights)

tmp7 <- mutate(flights, 
dep_time_2 = (dep_time %/% 100 * 60) +  (dep_time %% 100),
arr_time_2 = (arr_time %/% 100 * 60) +  (arr_time %% 100), 
air_time_2 = arr_time_2 - dep_time_2
)

select(tmp7, dep_time_2, arr_time_2, air_time_2, air_time)

###### 
dim(flights)
mutate(flights,
       air_time2 = arr_time - dep_time,
       air_time_diff = air_time2 - air_time) %>%
  filter(air_time_diff != 0) %>%
  select(air_time, air_time2, dep_time, arr_time, dest) 

```

3) Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
```{r}
select(flights, dep_time, sched_dep_time, dep_delay)
flights$dep_delay == flights$sched_dep_time - flights$dep_time 

mutate(flights,
       dep_delay2 = dep_time - sched_dep_time) %>%
  filter(dep_delay2 != dep_delay) %>%
  select(dep_time, sched_dep_time, dep_delay, dep_delay2) 
?flights  
```

4) Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().
```{r}
mutate(flights,
       dep_delay_rank = min_rank(desc(dep_delay))) %>% 
  arrange(dep_delay_rank) %>% 
  filter(dep_delay_rank <= 10)    
```

5) What does 1:3 + 1:10 return? Why?
```{r}
# 1:3 + 1:10
1:3
1:10
11:20 + 1:10 # because they need to be vectorized 
```

6) What trigonometric functions does R provide?
```{r}
# All the classics: cos, sin, tan, acos, asin, atan, plus a few others that are drive by numerical or computational issues
```








