---
title: "many_models_list_columns"
author: "Ruijuan Li"
date: "10/31/2017"
output: 
  html_document: 
    keep_md: yes
---

refer to https://jrnold.github.io/e4qf/many-models.html 
### 25.2.5 Exercises

1. A linear trend seems to be slightly too simple for the overall trend. Can you do better with a quadratic polynomial? How can you interpret the coefficients of the quadratic? (Hint you might want to transform year so that it has mean zero.)

```{r}
library(modelr)
library(tidyverse)
library("gapminder") 

country_model <- function(df) {
  lm(lifeExp ~ poly(year - median(year), 2), data = df)
}

by_country <- gapminder %>% 
  group_by(country, continent) %>% 
  nest()

by_country <- by_country %>%
  mutate(model = map(data, country_model))

by_country <- by_country %>% 
  mutate(
    resids = map2(data, model, add_residuals)
  )
by_country

unnest(by_country, resids) %>%
ggplot(aes(year, resid)) +
  geom_line(aes(group = country), alpha = 1 / 3) + 
  geom_smooth(se = FALSE)

by_country %>% 
  mutate(glance = map(model, broom::glance)) %>%
  unnest(glance, .drop = TRUE) %>%
  ggplot(aes(continent, r.squared)) +
  geom_jitter(width = 0.5) 
```

2. Explore other methods for visualising the distribution of R square per continent. You might want to try the ggbeeswarm package, which provides similar methods for avoiding overlaps as jitter, but uses deterministic methods.
```{r}
library("ggbeeswarm")
by_country %>% 
  mutate(glance = map(model, broom::glance)) %>%
  unnest(glance, .drop = TRUE) %>%
  ggplot(aes(continent, r.squared)) +
  geom_beeswarm()
```

3. To create the last plot (showing the data for the countries with the worst model fits), we needed two steps: we created a data frame with one row per country and then semi-joined it to the original dataset. It’s possible avoid this join if we use unnest() instead of unnest(.drop = TRUE). How? 
```{r}
by_country <- gapminder %>% 
  group_by(country, continent) %>% 
  nest() 

country_model <- function(df) {
  lm(lifeExp ~ year, data = df)
}

models <- map(by_country$data, country_model)

by_country <- by_country %>% 
  mutate(model = map(data, country_model))

by_country <- by_country %>% 
  mutate(
    resids = map2(data, model, add_residuals)
  )

glance <- by_country %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance) # drop unrelated columns 

bad_fit <- filter(glance, r.squared < 0.25)

gapminder %>% 
  semi_join(bad_fit, by = "country") %>% 
  ggplot(aes(year, lifeExp, colour = country)) +
    geom_line()

bad_fit %>% 
  unnest(data) %>%
  ggplot(aes(year, lifeExp, colour = country)) +
    geom_line() 
```

### 25.4.5 Exercises

1. List all the functions that you can think of that take a atomic vector and return a list.

2. Brainstorm useful summary functions that, like quantile(), return multiple values.

3. What’s missing in the following data frame? How does quantile() return that missing piece? Why isn’t that helpful here?

```{r}
mtcars %>% 
  group_by(cyl) %>% 
  summarise(q = list(quantile(mpg))) %>% 
  unnest()
#> # A tibble: 15 × 2
#>     cyl     q
#>   <dbl> <dbl>
#> 1     4  21.4
#> 2     4  22.8
#> 3     4  26.0
#> 4     4  30.4
#> 5     4  33.9
#> 6     6  17.8
#> # ... with 9 more rows
```

4. What does this code do? Why might might it be useful?

```{r}
mtcars %>% 
  group_by(cyl) %>% 
  summarise_each(funs(list)) 
```