---
title: "Assignment_07_19_2017"
author: "Ruijuan Li"
date: "7/18/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
library(stringr)
```

# 14.3.1.1 Exercises

1. Explain why each of these strings don’t match a \: "\", "\\", "\\\".
* "\": This will escape the next character in the R string.
* "\\": This will resolve to \ in the regular expression, which will escape the next character in the regular expression.
* "\\\": The first two backslashes will resolve to a literal backslash in the regular expression, the third will escape the next character. So in the regular expresion, this will escape some escaped character. 
```{r}
x1 <- "a\\b"
writeLines(x)

x <- "a\b"
writeLines(x)

x <- "a\\\b"
writeLines(x)

x <- "a\\\\b"
writeLines(x)

#> a\b 
str_view(x1, "\\\\") 
```

2. How would you match the sequence "'\?
```{r}
x <- "\"\'\\"
writeLines(x)

str_view(x, "\"\'\\\\") 
```

3. What patterns will the regular expression \..\..\.. match? How would you represent it as a string?

      It will match any patterns that are a dot followed by any character, repeated three times. (???)

# 14.3.2.1 Exercises

1. How would you match the literal string "$^$"?
```{r}
x <- "$^$"
writeLines(x)

str_view(x, "^\\$\\^\\$$")
```

2. Given the corpus of common words in stringr::words, create regular expressions that find all words that:

      1. Start with “y”.
      2. End with “x”
      3. Are exactly three letters long. (Don’t cheat by using str_length()!)
      4. Have seven letters or more.

```{r}
str_view(c("yes", "happy"), "^y")
str_view(c("tax", "xmas"), "x$")
str_view(c("tax", "xmas"), "^[a-zA-Z]{3}$")
str_view(c("birthday", "today", "Christmas"), "^[a-zA-Z]{7,}$")
```

Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.

# 14.3.3.1 Exercises

1. Create regular expressions to find all words that:

      1. Start with a vowel.

      2. That only contain consonants. (Hint: thinking about matching “not”-vowels.)

      3. End with ed, but not with eed.

      4. End with ing or ise.
      
```{r}
str_view(c("birthday", "Auburn", "earth", "iMac", "ohh", "Urea"), "^[aeiouAEIOU]")

str_view(c("birthday", "Auburn", "earth", "iMac", "ohh", "Urea"), "^[a|e|i|o|u|A|E|I|O|U]")

str_view(c("birthday", "Auburn", "earth", "iMac", "ohh", "Urea"), "^[^a|e|i|o|u|A|E|I|O|U]")

str_view(c("led", "let", "seed"), "[^e]ed$")

str_view(c("ending", "rise", "seed"), "ise$|ing$") 
```

2. Empirically verify the rule “i before e except after c”.

3. Is “q” always followed by a “u”?
```{r}
str_view(stringr::words, "qu", match = T)
```

4. Write a regular expression that matches a word if it’s probably written in British English, not American English.
https://jrnold.github.io/e4qf/strings.html

5. Create a regular expression that will match telephone numbers as commonly written in your country.
```{r}
x <- c("123-456-7890", "1235-2351")
str_view(x, "\\d\\d\\d-\\d\\d\\d-\\d\\d\\d\\d")
```

# 14.3.4.1 Exercises

1. Describe the equivalents of ?, +, * in {m,n} form.
```{r}
str_view(c("birthday", "today", "Christmas", "happy", "happpy"), "(p)?")
str_view(c("birthday", "today", "Christmas", "happy", "happpy"), "p?") 
```

2. Describe in words what these regular expressions match: (read carefully to see if I’m using a regular expression or a string that defines a regular expression.)

      ^.*$
      "\\{.+\\}"
      \d{4}-\d{2}-\d{2}
      "\\\\{4}"
      
3. Create regular expressions to find all words that:

      Start with three consonants.
      Have three or more vowels in a row.
      Have two or more vowel-consonant pairs in a row.

4. Solve the beginner regexp crosswords at https://regexcrossword.com/challenges/beginner.




