---
title: "Assignment_07_19_2017"
author: "Ruijuan Li"
date: "7/18/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
library(stringr)
```

# 14.3.1.1 Exercises

1. Explain why each of these strings don’t match a \: "\", "\\", "\\\".
* "\": This will escape the next character in the R string.
* "\\": This will resolve to \ in the regular expression, which will escape the next character in the regular expression.
* "\\\": The first two backslashes will resolve to a literal backslash in the regular expression, the third will escape the next character. So in the regular expresion, this will escape some escaped character. 
```{r}
x1 <- "a\\b"
writeLines(x1)

x <- "a\b"
writeLines(x)

x <- "a\\\b"
writeLines(x)

x <- "a\\\\b"
writeLines(x)

#> a\b 
str_view(x1, "\\\\") 
```

2. How would you match the sequence "'\?
```{r}
x <- "\"\'\\"
writeLines(x)

str_view(x, "\"\'\\\\") 
```

3. What patterns will the regular expression \..\..\.. match? How would you represent it as a string?

      It will match any patterns that are a dot followed by any character, repeated three times. (???)

# 14.3.2.1 Exercises

1. How would you match the literal string "$^$"?
```{r}
x <- "$^$"
writeLines(x)

str_view(x, "^\\$\\^\\$$")
```

2. Given the corpus of common words in stringr::words, create regular expressions that find all words that:

      1. Start with “y”.
      2. End with “x”
      3. Are exactly three letters long. (Don’t cheat by using str_length()!)
      4. Have seven letters or more.

```{r}
str_view(c("yes", "happy"), "^y")
str_view(c("tax", "xmas"), "x$")
str_view(c("tax", "xmas"), "^[a-zA-Z]{3}$")
str_view(c("birthday", "today", "Christmas"), "^[a-zA-Z]{7,}$")
```

Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.

# 14.3.3.1 Exercises

1. Create regular expressions to find all words that:

      1. Start with a vowel.

      2. That only contain consonants. (Hint: thinking about matching “not”-vowels.)

      3. End with ed, but not with eed.

      4. End with ing or ise.
      
```{r}
str_view(c("birthday", "Auburn", "earth", "iMac", "ohh", "Urea"), "^[aeiouAEIOU]")

str_view(c("birthday", "Auburn", "earth", "iMac", "ohh", "Urea"), "^[a|e|i|o|u|A|E|I|O|U]")

str_view(c("birthday", "Auburn", "earth", "iMac", "ohh", "Urea"), "^[^a|e|i|o|u|A|E|I|O|U]")

str_view(c("led", "let", "seed"), "[^e]ed$")

str_view(c("ending", "rise", "seed"), "ise$|ing$") 
```

2. Empirically verify the rule “i before e except after c”.

3. Is “q” always followed by a “u”?
```{r}
str_view(stringr::words, "qu", match = T)
```

4. Write a regular expression that matches a word if it’s probably written in British English, not American English.
https://jrnold.github.io/e4qf/strings.html

5. Create a regular expression that will match telephone numbers as commonly written in your country.
```{r}
x <- c("123-456-7890", "1235-2351")
str_view(x, "\\d\\d\\d-\\d\\d\\d-\\d\\d\\d\\d")
```

# 14.3.4.1 Exercises

1. Describe the equivalents of ?, +, * in {m,n} form.
```{r}
str_view(c("birthday", "today", "Christmas", "happy", "happpy"), "(p)?")
str_view(c("birthday", "today", "Christmas", "happy", "happpy"), "p?") 
```

2. Describe in words what these regular expressions match: (read carefully to see if I’m using a regular expression or a string that defines a regular expression.)

      ^.*$
      "\\{.+\\}"
      \d{4}-\d{2}-\d{2}
      "\\\\{4}"
      
3. Create regular expressions to find all words that:

      Start with three consonants.
      Have three or more vowels in a row.
      Have two or more vowel-consonant pairs in a row.

4. Solve the beginner regexp crosswords at https://regexcrossword.com/challenges/beginner.

###################################################### 
# 14.4.2 Exercises

1. For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls.

      1. Find all words that start or end with x.

      2. Find all words that start with a vowel and end with a consonant.

      3. Are there any words that contain at least one of each different vowel?

```{r}
words[str_detect(words, "^x|x$")] 
words[str_detect(words, "^x") | str_detect(words, "x$")]

str_subset(words, "^[aeiou].*[^aeiou]$") # * as and? don't know this before... 
words[str_detect(words, "^[aeiou]") & str_detect(words, "[^aeiou]$")]

words[str_detect(words, "a*e*i*o*u")] %>% head() # why this doesn't work... 
words[str_detect(words, "a") &
        str_detect(words, "e") &
        str_detect(words, "i") &
        str_detect(words, "o") &
        str_detect(words, "u")]
```

2. What word has the highest number of vowels? What word has the highest proportion of vowels? (Hint: what is the denominator?)
```{r} 
  # mutate(vowel_count = str_count(words, "[aeiou]")) %>%
  # arrange(desc(vowel_count)) %>%
  # head()

# words1 %>% 
#   mutate(vowel_count = str_count(words, "[aeiou]"),
#          vowel_perc = vowel_count/str_count(words)) %>%
#   arrange(desc(vowel_perc)) %>%
#   head() 
```

# 14.4.3.1 Exercises

1. In the previous example, you might have noticed that the regular expression matched “flickered”, which is not a colour. Modify the regex to fix the problem.

don't understand the question, where is the problem and where is the "previous example"? 

2. From the Harvard sentences data, extract:

      1. The first word from each sentence.
      2. All words ending in ing.
      3. All plurals.

```{r}
# 1) 
length(sentences)
str_extract(sentences, "^\\w+")  
str_view(sentences, "^\\w+")  

str_extract(sentences, "\\b[A-Za-z]+ing\\b")
str_view(sentences, "\\b[A-Za-z]+ing\\b")
# how to match any word... 

str_extract(sentences, "\\b[A-Za-z]+s\\b")
str_view(sentences, "\\b[A-Za-z]+es\\b|\\b[A-Za-z]+s\\b")
```

# 10.4.4.1 Exercises

1. Find all words that come after a “number” like “one”, “two”, “three” etc. Pull out both the number and the word.
I’ll use the same following “word” pattern as used above
```{r}
numword <- "(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
sentences[str_detect(sentences, numword)]  %>%
   str_extract(numword)
```

2. Find all contractions. Separate out the pieces before and after the apostrophe.
```{r}
str_view("I'm", "\'")

contr <- "([^ ]+)(\')([^ ]+)"
  
sentences[str_detect(sentences, contr)] %>% 
  str_extract(contr) 
```

# 14.4.5.1 Exercises

1. Replace all forward slashes in a string with backslashes.
```{r}
str_replace_all("a\\b, c\\d", "\\\\", "/")
```

2. Implement a simple version of str_to_lower() using replace_all().
```{r}
str_to_lower("ABCDE")
# leave this... 
```

3. Switch the first and last letters in words. Which of those strings are still words?
```{r}
str_view(words, "^[[:alpha:]]+")
str_view(words, "[[:alpha:]]+$")

x <- 'The quick brown fox'
str_view(x, "[[:alpha:]]+$")

# why ... skip... 
```

# 14.4.6.1 Exercises

1. Split up a string like "apples, pears, and bananas" into individual components.
```{r}
x <- c("apples, pears, and bananas")
# str_split(x, " ")  
```

2. Why is it better to split up by boundary("word") than " "?

3. What does splitting with an empty string ("") do? Experiment, and then read the documentation. 

# 14.5.1 Exercises

1. How would you find all strings containing \ with regex() vs. with fixed()?

2. What are the five most common words in sentences?

# 14.7.1 Exercises

1. Find the stringi functions that:

      1. Count the number of words.
      2. Find duplicated strings.
      3. Generate random text.
2. How do you control the language that stri_sort() uses for sorting?









