---
title: "Assignment_07_12_2017"
author: "Ruijuan Li"
date: "7/12/2017"
output: 
  html_document: 
    keep_md: yes
---

# 14.2.5 Exercises

1. In code that doesn’t use stringr, you’ll often see paste() and paste0(). What’s the difference between the two functions? What stringr function are they equivalent to? How do the functions differ in their handling of NA?
```{r}
library(tidyverse)
library(stringr)
?stringr
?paste # Concatenate vectors after converting to character. 

## When passing a single vector, paste0 and paste work like as.character.
paste0(1:12)
paste(1:12)        # same
as.character(1:12) # same

## If you pass several vectors to paste0, they are concatenated in a
## vectorized way.
(nth <- paste0(1:12, c("st", "nd", "rd", rep("th", 9))))
(nth <- paste(1:12, c("st", "nd", "rd", rep("th", 9))))
## paste works the same, but separates each input with a space.

?str_join
str_c(1:12) 
```

2. In your own words, describe the difference between the sep and collapse arguments to str_c().
```{r}
# sep is to specify the symbol used between different strings
# collapse is the symbol used in between words of a single string.  
```

3. Use str_length() and str_sub() to extract the middle character from a string. What will you do if the string has an even number of characters?
```{r}
?str_length
?str_sub

string_eg <- str_c(letters, collapse = "")
str_length(string_eg)/2

extract.middle <- function(string){
  if (length(string) %% 2 == 0){ 
  middle_vlaue <- str_sub(string, str_length(string)/2, str_length(string)/2+1)}
  else {
    middle_vlaue <- str_sub(string, str_length(string)/2+1, str_length(string)/2+1)
  return(middle_vlaue)
  }
  }  

extract.middle(string = string_eg)
```

4. What does str_wrap() do? When might you want to use it?
```{r}
# This is a wrapper around stri_wrap which implements the Knuth-Plass paragraph wrapping algorithm.
# would be useful when parse a paragraph
?str_wrap
thanks_path <- file.path(R.home("doc"), "THANKS")
thanks <- str_c(readLines(thanks_path), collapse = "\n")
thanks <- word(thanks, 1, 3, fixed("\n\n"))
cat(str_wrap(thanks), "\n")
cat(str_wrap(thanks, width = 40), "\n")
cat(str_wrap(thanks, width = 60, indent = 2), "\n")
cat(str_wrap(thanks, width = 60, exdent = 2), "\n")
cat(str_wrap(thanks, width = 0, exdent = 2), "\n") 
```

5. What does str_trim() do? What’s the opposite of str_trim()?
```{r}
?str_trim # Trim whitespace from start and end of string. 
str_trim("  String with trailing and leading white space\t")
str_trim("  String with trailing and leading white space    ")

str_pad("hadley", 3)
str_pad("a", c(5, 10, 20)) # adding space 
```

6. Write a function that turns (e.g.) a vector c("a", "b", "c") into the string a, b, and c. Think carefully about what it should do if given a vector of length 0, 1, or 2.
```{r}
vec_to_str <- function(vector){
  str_c(vector, collapse = "")
}

vec_to_str(letters) # don't really see 
```

https://regexone.com/ regular expression 

# 14.3.5.1 Exercises

1. Describe, in words, what these expressions will match:

      1. (.)\1\1
      2. "(.)(.)\\2\\1"
      3. (..)\1
      4. "(.).\\1.\\1"
      5. "(.)(.)(.).*\\3\\2\\1"
```{r}
# from Julin 
str_view("appple","(.)\\1\\1") # a tripple repeated single letter 
str_view("abba is my favorite band", "(.)(.)\\2\\1") # two different letters repeat for 1:2:2 
str_view("abab is my favorite band", "(..)\\1") # A two character string repeated , ie "abab"
str_view("bananas are good", "(.).\\1.\\1") # A character repeated twice, but with any other characters inbetween 
str_view("geese from canda see many sights","(.)(.)(.).*\\3\\2\\1") # A three character palindrome separated by any number of characters in the middle 
```

2. Construct regular expressions to match words that:

      1. Start and end with the same character.

      2. Contain a repeated pair of letters (e.g. “church” contains “ch” repeated twice.) 
```{r}
pattern <- "[A-Za-z]*([A-Za-z]{2})[a-z]*\\1[a-z]*"
str_view_all("what silly sentence am I going to write for this exercise?",pattern)
```

      3. Contain one letter repeated in at least three places (e.g. “eleven” contains three “e”s.)
```{r}
pattern <- "[A-Za-z]*([A-Za-z])[a-z]*\\1[a-z]*\\1[a-z]*"
str_view_all("what silly sentence am I going to write for this exercise?  Aiyeee",pattern) 
```

