---
title: "Assignment_09_27_2017"
author: "Ruijuan Li"
date: "9/27/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
library(modelr)
```

23.3.3 Exercises

1. Instead of using lm() to fit a straight line, you can use loess() to fit a smooth curve. Repeat the process of model fitting, grid generation, predictions, and visualisation on sim1 using loess() instead of lm(). How does the result compare to geom_smooth()?
```{r}
sim1_mod <- lm(y ~ x, data = sim1)
sim2_mod <- loess(y ~ x, data = sim1)

grid1 <- sim1 %>% 
  data_grid(x)

grid1 <- grid1 %>% 
  add_predictions(sim1_mod) 

ggplot(sim1, aes(x)) +
  geom_point(aes(y = y)) +
  geom_line(aes(y = pred), data = grid1, colour = "red", size = 1) 

grid2 <- sim1 %>% 
  data_grid(x)

grid2 <- grid1 %>% 
  add_predictions(sim2_mod) 

ggplot(sim1, aes(x)) +
  geom_point(aes(y = y)) +
  geom_line(aes(y = pred), data = grid2, colour = "red", size = 1) 

ggplot(sim1) + 
  geom_point(aes(x = x, y=y)) + 
  geom_smooth(mapping = aes(x = x, y = y))

# loess is more similar to geom_smooth 
?loess # Local Polynomial Regression Fitting: Fit a polynomial surface determined by one or more numerical predictors, using local fitting. 
```

2. add_predictions() is paired with gather_predictions() and spread_predictions(). How do these three functions differ?
```{r}
# Add predictions to a data frame

df <- tibble::data_frame(
  x = sort(runif(100)),
  y = 5 * x + 0.5 * x ^ 2 + 3 + rnorm(length(x))
)
plot(df)

m1 <- lm(y ~ x, data = df)
grid <- data.frame(x = seq(0, 1, length = 10))
grid %>% add_predictions(m1)

m2 <- lm(y ~ poly(x, 2), data = df)
grid %>% spread_predictions(m1, m2) # add one column for each model
grid %>% gather_predictions(m1, m2) # add prediction but in long format 
```

3. What does geom_ref_line() do? What package does it come from? Why is displaying a reference line in plots showing residuals useful and important?
```{r}
?geom_ref_line # add a reference line, came with package modelr. 
# the importance is to see residuals are evenly spread across the reference line. 
```

4. Why might you want to look at a frequency polygon of absolute residuals? What are the pros and cons compared to looking at the raw residuals?
```{r}
# we are expecting a normal distribution of residual. mostly 0 and less and less when they are deviated from 0. 
```





