---
title: "Assignment_09_12_2017"
author: "Ruijuan Li"
date: "9/12/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
library(nycflights13)
```

### 21.5.3 Exercises

1. Write code that uses one of the map functions to:

      1. Compute the mean of every column in mtcars.
      2. Determine the type of each column in nycflights13::flights.
      3. Compute the number of unique values in each column of iris.
      4. Generate 10 random normals for each of μ= −10, 0, 10, and 100.
      
```{r}
# 1) 
map(mtcars, mean)

# 2)
map(flights, typeof)

# 3) 
map(iris, unique) %>% map(length)

# 4) 
map(c(-10, 0, 10, 100), function(i) rnorm(n = 10, mean = i))
```

2. How can you create a single vector that for each column in a data frame indicates whether or not it’s a factor?
```{r}
map_lgl(mtcars, is.factor) # ??? don't understand the Q. 
```

3. What happens when you use the map functions on vectors that aren’t lists? What does map(1:5, runif) do? Why?
```{r}
map(1:5, runif) 
?map
```
still gives list output, because "map() returns a list"

4. What does map(-2:2, rnorm, n = 5) do? Why? What does map_dbl(-2:2, rnorm, n = 5) do? Why?
```{r, error=TRUE}
map(-2:2, rnorm, n = 5) # generate 5 normal number using mean from -2 to 2, output as a list 
map_dbl(-2:2, rnorm, n = 5)  
map_dbl(-2:2, rnorm, n = 1) 
# map_dbl() returns a double vector which is the same length as the input, when n is 5, map_dbl() cannot satisfy both 
```

5. Rewrite map(x, function(df) lm(mpg ~ wt, data = df)) to eliminate the anonymous function.
```{r}
mtcars %>% 
  split(.$cyl) %>% 
  map(function(df) lm(mpg ~ wt, data = df)) 

mtcars %>% 
  split(.$cyl) %>% 
  map(~lm(mpg ~ wt, data = .))  
```

### 21.9.3 Exercises

1. Implement your own version of every() using a for loop. Compare it with purrr::every(). What does purrr’s version do that your version doesn’t?
```{r}
x <- list(1:5, letters, list(10))

x %>% 
  every(is_character)

for (i in x){
  if(is_character(i)){
    print("T")
  } else {
    print("F")
  }
}
```

2. Create an enhanced col_sum() that applies a summary function to every numeric column in a data frame.
```{r}
col_sum <- function(df, f){
  keep(df, is.numeric) %>% summary()
}

col_sum(nycflights13::flights)
```

3. A possible base R equivalent of col_sum() is:

```{r}
col_sum3 <- function(df, f) {
  is_num <- sapply(df, is.numeric)
  df_num <- df[, is_num]
  sapply(df_num, f) # apply f function to each numeric column 
} 

col_sum4 <- function(df, f) {
  df_num <- keep(df, is.numeric) 
  map_dbl(df_num, f)
} 
```

But it has a number of bugs as illustrated with the following inputs:

```{r, error=TRUE}
df <- tibble(
  x = 1:3, 
  y = 3:1,
  z = c("a", "b", "c")
)
# OK
col_sum3(df, mean) 
# Has problems: don't always return numeric vector
col_sum3(df[1:2], mean) 
col_sum3(df[1], mean) 
col_sum3(df[0], mean) 

col_sum4(df, mean) %>% typeof() 
col_sum4(df[1:2], mean)
col_sum4(df[1], mean)
col_sum4(df[0], mean)  
```

What causes the bugs?
