---
title: "Assignment_06_28_2017"
author: "Ruijuan Li"
date: "7/14/2017"
output: 
  html_document: 
    keep_md: yes
---

# 13.3.1 Exercises

1. Add a surrogate key to flights.
```{r}
library(tidyverse)
library(nycflights13)

flights_2 <- 
flights %>%
  mutate(key = row_number(flights$month)) 
```

2. Identify the keys in the following datasets

      1. Lahman::Batting,
      2. babynames::babynames
      3. nasaweather::atmos
      4. fueleconomy::vehicles
      5. ggplot2::diamonds
      (You might need to install some packages and read some documentation.)
      
```{r}
library(Lahman)
library(babynames)
library(nasaweather)
library(fueleconomy)

?Batting # no primary key 
keyID <- which(lapply(colnames(Batting), function(x) {Batting %>% count(Batting[,x]) %>% select(n) %>% unique() %>% nrow()}) %>% unlist() == 1)
colnames(Batting)[keyID]

?babynames
colnames(babynames)
head(babynames)

babynames %>% 
  count(year, sex, name) %>%
  filter(nn > 1)

?atmos
atmos %>% 
  count(lat, long, year, month) %>%
  filter(n > 1)

?vehicles
vehicles %>%
  count(id) %>%
  filter(n > 1)

?diamonds
diamonds %>%
  count(carat, cut, color, clarity, x, y, z, depth, table, price) %>%
  filter(n > 1)
# no key 
```

3. Draw a diagram illustrating the connections between the Batting, Master, and Salaries tables in the Lahman package. Draw another diagram that shows the relationship between Master, Managers, AwardsManagers.

How would you characterise the relationship between the Batting, Pitching, and Fielding tables?
```{r}
# From Julin
# devtools::install_github("bergant/datamodelr")
library(datamodelr) 
# https://github.com/bergant/datamodelr 
```



