---
title: "Assignment_05_17_2017"
author: "Ruijuan Li"
date: "5/17/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(nycflights13)
library(tidyverse)
# summarise() group_by() 
```

## 5.6.7 Exercises

# 1) Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:

A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time.
```{r}
flights %>%
  group_by(flight) %>%
  summarize(early_15_min = sum(arr_delay == -15, na.rm = TRUE) / n(),
            late_15_min = sum(arr_delay == 15, na.rm = TRUE) / n()) %>%
  filter(early_15_min == 0.5,
         late_15_min == 0.5)
```

A flight is always 10 minutes late.
```{r}
group_by(flights, flight) %>% 
  filter(arr_delay == 10) %>%
  select(flight) 
```

A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.
```{r}
flights %>%
  group_by(flight) %>%
  summarize(early_15_min = sum(arr_delay == -30, na.rm = TRUE) / n(),
            late_15_min = sum(arr_delay == 30, na.rm = TRUE) / n()) %>%
  filter(early_15_min == 0.5,
         late_15_min == 0.5)
```

99% of the time a flight is on time. 1% of the time it’s 2 hours late.
```{r}
flights %>%
  group_by(flight) %>%
  summarize(early_15_min = sum(arr_delay == 0, na.rm = TRUE) / n(),
            late_15_min = sum(arr_delay >= 120, na.rm = TRUE) / n()) %>%
  filter(early_15_min == 0.99,
         late_15_min == 0.01)
```

Which is more important: arrival delay or departure delay?
```{r}
# don't understand the question 
```

# 2) Come up with another approach that will give you the same output as not_cancelled %>% count(dest) and not_cancelled %>% count(tailnum, wt = distance) (without using count()).
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% 
  count(dest)

group_by(not_cancelled, dest) %>% 
  summarise(n())

not_cancelled %>%
  count(tailnum, wt = distance)

group_by(not_cancelled, tailnum) %>%
  summarise(sum(distance)) 
```

# 3) Our definition of cancelled flights (is.na(dep_delay) | is.na(arr_delay) ) is slightly suboptimal. Why? Which is the most important column?
```{r}
colnames(flights) 
summary(flights)
```

# 4) Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?
```{r} 
tmp <- group_by(flights, year, month, day) %>% 
  summarise(cancel = sum(is.na(dep_delay) | is.na(arr_delay)),
            delay = mean(arr_delay, na.rm=T)) 

cor.test(tmp$cancel, tmp$delay) # positively correlated
plot(tmp$cancel, tmp$delay)
```

# 5) Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))
```{r}
flights %>% 
  group_by(carrier, dest) %>%
  summarise(n(), 
            delay = mean(arr_delay, na.rm=T)) %>% 
  arrange(desc(delay)) 

flights %>% 
  group_by(carrier, dest) %>%
  summarise(n(), 
            delay = mean(arr_delay, na.rm=T)) %>% 
  arrange(desc(delay)) %>% 

# when don't consider dest 
flights %>% 
  group_by(carrier) %>%
  summarise(n(), 
            delay = mean(arr_delay, na.rm=T)) %>% 
  arrange(desc(delay)) 
# F9 has the worst delay  
```

# 6) What does the sort argument to count() do. When might you use it?
```{r}
?count
# copied from somewhere: The sort argument to count() sorts by descending order of n. This is useful because often the most common group is the most important. 
```

## 5.7.1 Exercises

# 1) Refer back to the lists of useful mutate and filtering functions. Describe how each operation changes when you combine it with grouping. 
```{r}
# mutate & filtering will work within each group.  
```

# 2) Which plane (tailnum) has the worst on-time record?
```{r}
flights %>% 
  group_by(tailnum) %>% 
  summarise(delay = mean(arr_delay, na.rm=T)) %>%
  arrange(desc(delay)) 
```

# 3) What time of day should you fly if you want to avoid delays as much as possible?
```{r}
flights %>% 
  group_by(year, month, day, time_hour) %>% 
  summarise(delay = mean(arr_delay, na.rm=T)) %>% 
  arrange(delay) 
```

# 4) For each destination, compute the total minutes of delay. For each, flight, compute the proportion of the total delay for its destination.
```{r}
flights %>% 
  group_by(dest) %>%
  summarise(sum(arr_delay, na.rm=T))

flights %>% 
  group_by(flight) %>% 
  summarise(prop_delay = sum(arr_delay >= 0, na.rm = TRUE) / n()) 
```

# 5) Delays are typically temporally correlated: even once the problem that caused the initial delay has been resolved, later flights are delayed to allow earlier flights to leave. Using lag() explore how the delay of a flight is related to the delay of the immediately preceding flight.
```{r}
# ah, this is more complicated... 


```

# 6) Look at each destination. Can you find flights that are suspiciously fast? (i.e. flights that represent a potential data entry error). Compute the air time a flight relative to the shortest flight to that destination. Which flights were most delayed in the air?
```{r}
flights %>% 
  group_by(dest) %>% 
  summarise(air_time_ratio = (mean(air_time, na.rm=T)/min(air_time, na.rm=T))) 
```

# 7) Find all destinations that are flown by at least two carriers. Use that information to rank the carriers.
```{r}
flights %>% 
  group_by(dest) %>% 
  summarise(unique_carrier = length(unique(carrier))) %>% 
            filter(unique_carrier >= 2)  
```

# 8) For each plane, count the number of flights before the first delay of greater than 1 hour.
```{r}

```






