---
title: "Assignment_09_06_2017"
author: "Ruijuan Li"
date: "9/6/2017"
output: 
  html_document: 
    keep_md: yes
---

### 21.2.1 Exercises

1. Write for loops to:

      1. Compute the mean of every column in mtcars.
      2. Determine the type of each column in nycflights13::flights.
      3. Compute the number of unique values in each column of iris.
      4. Generate 10 random normals for each of μ=−10, 0, 10, and 100.
      
Think about the output, sequence, and body before you start writing the loop.
```{r}
library(tidyverse)

# 1) 
mean.mtcars <- vector()
for (i in colnames(mtcars)) {
  mean.mtcars[[i]] <- mean(mtcars[,i])  
}
mean.mtcars

# 2) 
type_flights <- vector()
for (i in colnames(nycflights13::flights)){
  type_flights[[i]] <- typeof(nycflights13::flights[[i]])
}
type_flights

# 3) 
uniq_num_iris <- vector()
for (i in colnames(iris)){
  uniq_num_iris[[i]] <- length(unique(iris[,i]))
}
uniq_num_iris

# 4) 
ran_norm <- list()
mean <- c(-10, 0, 10, 100)
for (i in seq_along(mean)){
  ran_norm[[i]] <- rnorm(n = 10, mean = mean[[i]])
}
ran_norm
```

2. Eliminate the for loop in each of the following examples by taking advantage of an existing function that works with vectors:

```{r}
# out <- ""
# for (x in letters) {
#   out <- stringr::str_c(out, x)
# }

# str_c(letters, collapse = "")

set.seed(1)
x <- sample(100)
sd <- 0
for (i in seq_along(x)) {
  sd <- sd + (x[i] - mean(x)) ^ 2
}
sd <- sqrt(sd / (length(x) - 1))

sd(x)

set.seed(1)
x <- runif(100)
out <- vector("numeric", length(x))
out[1] <- x[1]
for (i in 2:length(x)) {
  out[i] <- out[i - 1] + x[i]
}
out

cumsum(x)
```

3. Combine your function writing and for loop skills:

      1. Write a for loop that prints() the lyrics to the children’s song “Alice the camel”.

      2. Convert the nursery rhyme “ten in the bed” to a function. Generalise it to any number of people in any sleeping structure.

      3. Convert the song “99 bottles of beer on the wall” to a function. Generalise to any number of any vessel containing any liquid on any surface.
```{r}
lyrics <- read.delim("~/Desktop/2017_summer/Rclub-r4ds_Ruijuan.Li/R-club-Sep-06/lyrics", header = F, stringsAsFactors = F)

for (i in rownames(lyrics)){
  print(lyrics[i,])
} 

# skip... 
```

4. It’s common to see for loops that don’t preallocate the output and instead increase the length of a vector at each step:

```{r}
output <- vector("integer", 0)
system.time(
for (i in seq_along(x)) {
  output <- c(output, lengths(x[[i]]))
})

output <- vector()
system.time(
for (i in seq_along(x)) {
  output <- c(output, lengths(x[[i]]))
})

# how does this affect permformance? 
# system time? no. memory usage? ... skip 
```
How does this affect performance? Design and execute an experiment. 

### 21.3.5 Exercises

1. Imagine you have a directory full of CSV files that you want to read in. You have their paths in a vector, files <- dir("data/", pattern = "\\.csv$", full.names = TRUE), and now want to read each one with read_csv(). Write the for loop that will load them into a single data frame.
```{r}
# output <- data_frame() 
# files <- dir("data/", pattern = "\\.csv$", full.names = TRUE) 
# for (i in files){
#   output[[i]] <- read_csv(i) # something like this... 
# }
# output 

# a single data frame ? how??? 
```

2. What happens if you use for (nm in names(x)) and x has no names? What if only some of the elements are named? What if the names are not unique?
```{r, error=T}
# no name 
names(letters)

for (i in names(letters)){
  print(letters[[i]])
}

names(letters)[1:3] <- c("A", "B", "C")

for (i in names(letters)){
  print(letters[[i]])
}

names(letters) <- c(LETTERS[1:24], "A", "B")

for (i in names(letters)){
  print(letters[[i]])
}
```

3. Write a function that prints the mean of each numeric column in a data frame, along with its name. For example, show_mean(iris) would print:

```{r}
# show_mean(iris) 
#> Sepal.Length: 5.84
#> Sepal.Width:  3.06
#> Petal.Length: 3.76
#> Petal.Width:  1.20

iris %>% head()

show_mean <- function(input){
  output <- data.frame()
  for (i in colnames(input)){
    rownames()
    
  }  
}

```
(Extra challenge: what function did I use to make sure that the numbers lined up nicely, even though the variable names had different lengths?)

4. What does this code do? How does it work?

```{r}
trans <- list( 
  disp = function(x) x * 0.0163871,
  am = function(x) {
    factor(x, labels = c("auto", "manual"))
  }
)
for (var in names(trans)) {
  mtcars[[var]] <- trans[[var]](mtcars[[var]])
}
```










