---
title: "Assignment_08_30_2017"
author: "Ruijuan Li"
date: "8/30/2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
```

### 20.4.6 Exercises

1. What does mean(is.na(x)) tell you about a vector x? What about sum(!is.finite(x))?
```{r}
set.seed(1)
x <- runif(10, 1, 100)
x <- c(x, NA, -Inf)
x

mean(is.na(x)) # the proportion of missing data 
sum(!is.finite(x)) # the number of infinite in x  
```

2. Carefully read the documentation of is.vector(). What does it actually test for? Why does is.atomic() not agree with the definition of atomic vectors above?
```{r}
# two types of vectors: atomic & list, atomic vectors are homogeneous, list vectors are hetergeneous. 

?is.vector
# is.vector returns TRUE if x is a vector of the specified mode having no attributes other than names. It returns FALSE otherwise.

df <- data.frame(x = 1:3, y = 5:7)
is.list(df)
! is.vector(df$x)
is.vector(df$x)
is.vector(list())

?is.atomic 
# is.atomic returns TRUE if x is of an atomic type (or NULL) and FALSE otherwise.
is.atomic(df)
is.atomic(df$x)
is.atomic(list())
```

3. Compare and contrast setNames() with purrr::set_names().
```{r, warning=TRUE}
# setNames( 1:3, c("foo", "bar", "baz") )
# set_names(1:4, c("a", "b", "c", "d"))
# 
# # setNames(letters[1:5])
# set_names(letters[1:5]) # allow missing name 
# setNames(nm = c("First", "2nd")) # allow missing object
# set_names(nm = c("First", "2nd"))
```

4. Create functions that take a vector as input and returns:

      1. The last value. Should you use [ or [[?

      2. The elements at even numbered positions.

      3. Every element except the last value.

      4. Only even numbers (and no missing values).
      
```{r}
set.seed(1)
x <- sample(20, 100, replace = TRUE)
x <- c(x, NA)
x

# 1
last <- function(x){x[length(x)]}
last(x)

# 2 
even_pos <- function(x){
  pos <- sapply(1: length(x), function(i) i %% 2 ==0)
  x[pos]
  }
even_pos(x) 

# 3
drop_last <- function(x){x[1:length(x)-1]}
drop_last(x)

# 4
even <- function(x){
  x1 <- x[!is.na(x)]
  x1[x1 %% 2 == 0]}
even(x)
```

5. Why is x[-which(x > 0)] not the same as x[x <= 0]?
```{r}
x <- c(x, -4, -Inf)
x

x[-which(x > 0)] 
x[x <= 0] 
# why? 
```


6. What happens when you subset with a positive integer that’s bigger than the length of the vector? What happens when you subset with a name that doesn’t exist?
```{r}
length(x)
x[length(x) + 1]
x <- setNames(x, nm = c(1:length(x)))
x["104"]
```

### 20.5.4 Exercises

1 Draw the following lists as nested sets:

      1. list(a, b, list(c, d), list(e, f))
      2. list(list(list(list(list(list(a))))))
      
2. What happens if you subset a tibble as if you’re subsetting a list? What are the key differences between a list and a tibble?
```{r}
iris_tibble <- as_tibble(iris)
identical(iris_tibble[[1]], iris[[1]]) # return the same thing. 

# data structures of tibble and list are different. tibble is more like data frame whereas list is not.  
```

### 20.7.4 Exercises

1. What does hms::hms(3600) return? How does it print? What primitive type is the augmented vector built on top of? What attributes does it use?
```{r}
x <- hms::hms(3600)
x
attributes(x) 
typeof(x) # double 
```

2. Try and make a tibble that has columns with different lengths. What happens?
```{r, warning=TRUE}
# tb <- tibble::tibble(x = 1:5, y = 5:0)
```

3. Based on the definition above, is it ok to have a list as a column of a tibble?
```{r}
tb <- tibble::tibble(x = 1:5, y = 5:1, c = list(1:5))
# yes, as long as it is the same length as other columns
```



