---
title: "Assignment_05_23_2017"
author: "Ruijuan Li"
date: "5/23/2017"
output: 
  html_document: 
    keep_md: yes
---

7.3.4 Exercises

Explore the distribution of each of the x, y, and z variables in diamonds. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.
```{r}
library(tidyverse)
summary(diamonds)

ggplot(diamonds) + geom_histogram(mapping = aes(x=x), binwidth = 0.5)
ggplot(diamonds) + geom_histogram(mapping = aes(x=y), binwidth = 0.5)

ggplot(diamonds) + geom_histogram(mapping = aes(x=y), binwidth = 0.5) +  coord_cartesian(ylim = c(0, 50))

ggplot(diamonds) + geom_histogram(mapping = aes(x=z), binwidth = 0.5) + coord_cartesian(ylim = c(0, 2500))

ggplot(diamonds) + geom_histogram(mapping = aes(x=z)) + coord_cartesian(ylim = c(0, 2500))

# not very familiar with diamond... 
```

Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: Carefully think about the binwidth and make sure you try a wide range of values.)
```{r}
ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 1000)

diamonds %>% 
  count(cut_width(price, 1000)) 
?cut_width 

# most of the diamond's price fall between 500 to 1.5e+03
ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 100)
diamond_price_bin_100 <- diamonds %>% 
  count(cut_width(price, 100)) 

head(diamond_price_bin_100, 20)

# when have smaller bin, price ranged from 1450 to 1550 have suprisingly samll number of diamond 

ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 10)
# for a specific range, there is no diamond in that price range 
# zoom in 
ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 10) +  coord_cartesian(xlim = c(0, 2000))

ggplot(diamonds) + geom_histogram(aes(x=price)) +  coord_cartesian(xlim = c(0, 2000))


# no diamond is the price range around 1500, why? 
```

How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?
```{r}
ggplot(diamonds) + geom_histogram(mapping = aes(x=carat), binwidth = 0.01)
diamonds %>% 
  filter(carat == 0.99) %>%
    count()

diamonds %>% 
  filter(carat == 1) %>%
    count()

# people like 1 carate diamond 
```

Compare and contrast coord_cartesian() vs xlim() or ylim() when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?
```{r}
# see above, when you don't set binwidth, the default is bins = 30 
```

7.4.1 Exercises

What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?
```{r}
diamonds2 <- diamonds %>% 
  mutate(y = ifelse(y < 3 | y > 20, NA, y))

summary(diamonds2)

ggplot(data = diamonds2, mapping = aes(x = y)) + 
  geom_histogram(binwidth = 0.01)

ggplot(data = diamonds2, mapping = aes(x = carat, y = y)) + 
  geom_col()

# geom_col remove them bc they are missing, geom_histogram remove them because they are not finite values 
```

What does na.rm = TRUE do in mean() and sum()?
```{r}
numbers <- seq(1:100)
numbers
missing_data <- rep(NA, 10)
all <- c(numbers, missing_data)
all

mean(all)
mean(all, na.rm = T)

sum(all)
sum(all, na.rm = T)
# na.rm remove the missing value & their position in the data. so mean is only the mean of non-missing data devided by the number of non-missing data. 
```

7.5.1.1 Exercises

Use what you’ve learned to improve the visualisation of the departure times of cancelled vs. non-cancelled flights.
```{r}
# data
new <- 
  nycflights13::flights %>% 
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
  ) 

# the original 
ggplot(new, mapping = aes(sched_dep_time)) + 
    geom_freqpoly(mapping = aes(colour = cancelled), binwidth = 1/4)

# improved 
ggplot(new, mapping = aes(sched_dep_time, y = ..density..)) + 
    geom_freqpoly(mapping = aes(colour = cancelled), binwidth = 1/4)
```

What variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?
```{r}
library(reshape2)
summary(diamonds) 

diamonds.melt <- melt(diamonds, id.vars = "price")
head(diamonds.melt)
dim(diamonds.melt)

# ggplot(diamonds.melt, mapping = aes(price, y = value)) + 
#    geom_point() + facet_wrap(~variable)

# not a good way 
cor(diamonds$price, diamonds$carat)
cor(diamonds$price, diamonds$depth)
cor(diamonds$price, diamonds$table)
cor(diamonds$price, diamonds$x)
cor(diamonds$price, diamonds$y)
cor(diamonds$price, diamonds$z)

# carat has the highest correlation with price 
ggplot(data = diamonds, mapping = aes(x = cut, y = carat)) +
  geom_boxplot()
# the good diamond don't have high carat, higher carate diamond sells expensive 
```

Install the ggstance package, and create a horizontal boxplot. How does this compare to using coord_flip()?
```{r}
# install.packages("ggstance")
library(ggstance)

# with coord_flip
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy)) +
  coord_flip()

# with ggstance
ggplot(data = mpg) +
  geom_boxploth(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy))

ggplot(data = mpg) +
  geom_boxploth(mapping = aes(y = reorder(class, hwy, FUN = median), x = hwy))

# just need to flip the x & y coordinate 
```

One problem with boxplots is that they were developed in an era of much smaller datasets and tend to display a prohibitively large number of “outlying values”. One approach to remedy this problem is the letter value plot. Install the lvplot package, and try using geom_lv() to display the distribution of price vs cut. What do you learn? How do you interpret the plots?
```{r}
#install.packages("lvplot")

# library("lvplot")
# ggplot(diamonds, aes(x = cut, y = price)) +
#   geom_lv()
# package incompatibility, will fix later...  
```

Compare and contrast geom_violin() with a facetted geom_histogram(), or a coloured geom_freqpoly(). What are the pros and cons of each method?
```{r}
# discuss in class 
```

If you have a small dataset, it’s sometimes useful to use geom_jitter() to see the relationship between a continuous and categorical variable. The ggbeeswarm package provides a number of methods similar to geom_jitter(). List them and briefly describe what each one does.
```{r}
# install.packages("ggbeeswarm")
library(ggbeeswarm)
```

[see the examples] (https://jrnold.github.io/e4qf/exploratory-data-analysis.html#a-categorical-and-continuous-variable)

7.5.2.1 Exercises

How could you rescale the count dataset above to more clearly show the distribution of cut within colour, or colour within cut?
```{r}

```

Use geom_tile() together with dplyr to explore how average flight delays vary by destination and month of year. What makes the plot difficult to read? How could you improve it?
```{r}
library(nycflights13)
flights %>%
  group_by(month, dest) %>%
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = dest, fill = dep_delay)) +
  geom_tile() +
  labs(x = "Month", y = "Destination", fill = "Departure Delay")

# missing value, better color scheme 

library("viridis")
flights %>%
  group_by(month, dest) %>%
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = dest, fill = dep_delay)) +
  geom_tile() +
  scale_fill_viridis() +
  labs(x = "Month", y = "Destination", fill = "Departure Delay")

flights %>%
  group_by(month, dest) %>%
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = dest, fill = dep_delay)) +
  geom_tile() +
  scale_fill_gradient2(low="green", high="red") +
  labs(x = "Month", y = "Destination", fill = "Departure Delay") 
# also need to reorder 
```

Why is it slightly better to use aes(x = color, y = cut) rather than aes(x = cut, y = color) in the example above?
```{r}
diamonds %>% 
  count(color, cut) %>%  
  ggplot(mapping = aes(x = color, y = cut)) +
    geom_tile(mapping = aes(fill = n))

diamonds %>% 
  count(color, cut) %>%  
  ggplot(mapping = aes(x = cut, y = color)) +
    geom_tile(mapping = aes(fill = n))
# why??? 
```

7.5.3.1 Exercises

Instead of summarising the conditional distribution with a boxplot, you could use a frequency polygon. What do you need to consider when using cut_width() vs cut_number()? How does that impact a visualisation of the 2d distribution of carat and price?
```{r}
ggplot(data = diamonds, 
       mapping = aes(x = price,
                     colour = cut_width(carat, 0.3))) +
  geom_freqpoly()

ggplot(data = diamonds, 
       mapping = aes(x = price,
                     colour = cut_number(carat, 3))) +
  geom_freqpoly()
# cut_width define the bin size, cut_number define the number of bins 
```

Visualise the distribution of carat, partitioned by price.
```{r}
ggplot(diamonds, aes(x = cut_width(price, 1000), y = carat)) +
  geom_boxplot() +
  coord_flip() +
  xlab("Price") 
```

How does the price distribution of very large diamonds compare to small diamonds. Is it as you expect, or does it surprise you?
```{r}
ggplot(diamonds, aes(x = cut_width(carat, 0.5), y = price)) +
  geom_boxplot() +
  coord_flip()
# very large diamond are always expensive 
```

Combine two of the techniques you’ve learned to visualise the combined distribution of cut, carat, and price.
```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_point() +
  facet_wrap(~ cut, ncol = 1)

ggplot(diamonds, aes(x = carat, y = price)) +
  geom_hex() +
  facet_wrap(~ cut, ncol = 1)
```

Two dimensional plots reveal outliers that are not visible in one dimensional plots. For example, some points in the plot below have an unusual combination of x and y values, which makes the points outliers even though their x and y values appear normal when examined separately.

Why is a scatterplot a better display than a binned plot for this case?
```{r}

```

