---
title: "Assignment_05_23_2017"
author: "Ruijuan Li"
date: "5/23/2017"
output: 
  html_document: 
    keep_md: yes
---

7.3.4 Exercises

Explore the distribution of each of the x, y, and z variables in diamonds. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.
```{r}
library(tidyverse)
summary(diamonds)

ggplot(diamonds) + geom_histogram(mapping = aes(x=x), binwidth = 0.5)
ggplot(diamonds) + geom_histogram(mapping = aes(x=y), binwidth = 0.5)

ggplot(diamonds) + geom_histogram(mapping = aes(x=y), binwidth = 0.5) +  coord_cartesian(ylim = c(0, 50))

ggplot(diamonds) + geom_histogram(mapping = aes(x=z), binwidth = 0.5) + coord_cartesian(ylim = c(0, 2500))

ggplot(diamonds) + geom_histogram(mapping = aes(x=z)) + coord_cartesian(ylim = c(0, 2500))

# not very familiar with diamond... 
```

Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: Carefully think about the binwidth and make sure you try a wide range of values.)
```{r}
ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 1000)

diamonds %>% 
  count(cut_width(price, 1000)) 
?cut_width 

# most of the diamond's price fall between 500 to 1.5e+03
ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 100)
diamond_price_bin_100 <- diamonds %>% 
  count(cut_width(price, 100)) 

head(diamond_price_bin_100, 20)

# when have smaller bin, price ranged from 1450 to 1550 have suprisingly samll number of diamond 

ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 10)
# for a specific range, there is no diamond in that price range 
# zoom in 
ggplot(diamonds) + geom_histogram(aes(x=price), binwidth = 10) +  coord_cartesian(xlim = c(0, 2000))

ggplot(diamonds) + geom_histogram(aes(x=price)) +  coord_cartesian(xlim = c(0, 2000))


# no diamond is the price range around 1500, why? 
```

How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?
```{r}
ggplot(diamonds) + geom_histogram(mapping = aes(x=carat), binwidth = 0.01)
diamonds %>% 
  filter(carat == 0.99) %>%
    count()

diamonds %>% 
  filter(carat == 1) %>%
    count()

# people like 1 carate diamond 
```

Compare and contrast coord_cartesian() vs xlim() or ylim() when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?
```{r}
# see above, when you don't set binwidth, the default is bins = 30 
```

7.4.1 Exercises

What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?
```{r}
diamonds2 <- diamonds %>% 
  mutate(y = ifelse(y < 3 | y > 20, NA, y))

summary(diamonds2)

ggplot(data = diamonds2, mapping = aes(x = y)) + 
  geom_histogram(binwidth = 0.01)

ggplot(data = diamonds2, mapping = aes(x = carat, y = y)) + 
  geom_col()

# geom_col remove them bc they are missing, geom_histogram remove them because they are not finite values 
```

What does na.rm = TRUE do in mean() and sum()?
```{r}
numbers <- seq(1:100)
numbers
missing_data <- rep(NA, 10)
all <- c(numbers, missing_data)
all

mean(all)
mean(all, na.rm = T)

sum(all)
sum(all, na.rm = T)
# na.rm remove the missing value & their position in the data. so mean is only the mean of non-missing data devided by the number of non-missing data. 
```




